%-------------------------
% Resume — Akhil Shekkari
% Targeted: AI/ML Research Engineer roles at top labs
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[a4paper, top=0.3in, left=0.5in, right=0.5in, bottom=0.3in]{geometry}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheadingSingle}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Akhil Shekkari} \\ \vspace{1pt}
    \small
    \href{https://shekkari1999.github.io}{Portfolio} \textbar\
    \href{https://github.com/shekkari1999}{GitHub} \textbar\
    \href{https://www.linkedin.com/in/akhilshekkari/}{LinkedIn} \textbar\
    \href{mailto:shekkari.akhil@gmail.com}{shekkari.akhil@gmail.com} \textbar\
    +1 (425) 426-8292
\end{center}
\vspace{-0.55cm}

%-----------SUMMARY-----------
\section{Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item AI engineer with 3+ years of industry experience shipping RAG pipelines, LLM evaluation systems, and ML models to production. Deep hands-on expertise in \textbf{LLM post-training} (RLHF, GRPO), \textbf{agentic systems} (tool use, multi-step reasoning, MCP), and \textbf{inference optimization} (KV-cache, paged attention, Triton kernels).
  }
\end{itemize}
\vspace{-0.55cm}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingSingle
      {AI Engineer \textbar\ Atrium \textbar\ Silver Spring, USA}{June 2025 to August 2025}
      \resumeItemListStart
        \resumeItem{Automated \textbf{Statistical Analysis Plan (SAP)} generation from clinical trial documents for Pfizer's team, reducing drafting time by \textbf{up to 60\%}.}
        \resumeItem{Evaluated knowledge graphs, naive chunking, and semantic chunking strategies; benchmarked \textbf{embedding models} (OpenAI, BiomedBERT, Cohere) and \textbf{hybrid retrieval} (dense + BM25 sparse), and selected the best-performing RAG configuration on internal test sets.}
        \resumeItem{Built a custom \textbf{LLM-as-a-Judge} evaluation system with structured rubrics scoring completeness, guideline adherence, and hallucination detection against ground truth SAPs, achieving \textbf{82\% precision} and \textbf{78\% recall}.}
        \resumeItem{Ran \textbf{50+ prompt experiments} (temperature, system prompts, few-shot examples, input formatting), improving generation consistency by \textbf{20\%} and reducing manual revision cycles by \textbf{30\%}.}
      \resumeItemListEnd

    \resumeSubheadingSingle
      {Software Developer \textbar\ Tezo \textbar\ India}{July 2021 to July 2024}
      \resumeItemListStart
        \resumeItem{Built a \textbf{RAG-powered chatbot} over SharePoint repositories, giving \textbf{200+ employees} a unified search interface across \textbf{10k+ internal documents} with sub-second retrieval.}
        \resumeItem{Engineered a \textbf{semantic search pipeline} (embeddings + vector DB) reducing document lookup time by \textbf{60\%}, and added \textbf{LLM-based summarization} cutting manager review time by \textbf{35\%}.}
        \resumeItem{Trained \textbf{ML models} for insurance policy scoring and fraud detection, improving fraud recall by \textbf{15\%} and enabling earlier intervention across the claims pipeline.}
        \resumeItem{Containerized and deployed all services with \textbf{Docker + CI/CD} on secure on-prem infrastructure with \textbf{99.5\% uptime}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-0.15cm}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
      {\textbf{AI Agent Framework} {\small\href{https://github.com/shekkari1999/Agents}{GitHub}}}{2025}
      \resumeItemListStart
        \resumeItem{Built a \textbf{multi-step reasoning agent} from scratch: agentic loop with function calling, \textbf{MCP integration} for external tool servers, Pydantic-validated structured outputs, and sliding-window memory with compaction.}
        \resumeItem{Implemented \textbf{5+ tools} (web search, code execution, multi-format file handling) with callback-driven observability and session persistence via FastAPI.}
        \resumeItem{\textbf{LoRA fine-tuned Qwen 3B} for chat and function calling using \textbf{QLoRA} (4-bit NormalFloat), then replaced the OpenAI backbone with the fine-tuned model as the agent's reasoning engine.}
        \resumeItem{Evaluated on the \textbf{GAIA benchmark} (GPT-4o vs Claude vs fine-tuned Qwen), achieving competitive scores on Level 1 to 3 multi-step tasks.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Building a Reasoning LLM} {\small\href{https://github.com/shekkari1999/reasoning}{GitHub}}}{2025}
      \resumeItemListStart
        \resumeItem{Implemented the full \textbf{post-training pipeline} to turn a base LLM (Qwen-2.5) into a reasoning model: inference-time scaling, self-refinement, and \textbf{GRPO reinforcement learning} from raw PyTorch (no TRL).}
        \resumeItem{Scaled training with \textbf{FSDP} and \textbf{gradient accumulation} across multiple GPUs; implemented \textbf{data, tensor, and pipeline parallelism} strategies for efficient rollout generation and policy updates.}
        \resumeItem{Built custom inference engine with \textbf{KV-cache} and sampling, plus a math evaluation harness with \textbf{SymPy symbolic equivalence} on GSM8K and MATH benchmarks. Implemented \textbf{chain-of-thought, self-consistency}, and self-refinement.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Mini Inference Engine} {\small\href{https://github.com/shekkari1999/mini-Inference-engine-from-scratch}{GitHub}}}{2025}
      \resumeItemListStart
        \resumeItem{Built a modular LLM inference engine with \textbf{naive, streaming (online softmax), and Triton-fused attention} kernels, benchmarked across 4K to 16K token prefill and decode workloads.}
        \resumeItem{Designed \textbf{paged KV-cache} (on-demand allocation, zero fragmentation) achieving \textbf{O(T) memory} vs O(T\textsuperscript{2}) for naive. Quantified Triton kernel-fusion speedups over Python page loops.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item \textbf{Languages \& Frameworks:} Python, PyTorch, Triton, SQL, Pydantic, FastAPI, Gradio, LangChain, LlamaIndex
    \vspace{-0.2cm}
    \item \textbf{ML \& Training:} LoRA/QLoRA, FSDP, Hugging Face Transformers, Unsloth, W\&B, ClearML, Scikit-learn
    \vspace{-0.2cm}
    \item \textbf{Infrastructure:} Docker, Kubernetes, AWS SageMaker, Azure ML, Snowflake, GitHub Actions, CI/CD
  }
\end{itemize}
\vspace{-0.55cm}

%-----------EDUCATION-----------
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item \textbf{University of Maryland, College Park} \hfill Expected May 2026 \\
          Master of Science in Applied Machine Learning \\
          \textbf{Coursework:} Deep Learning, NLP, Advanced ML, Reinforcement Learning, Optimization, Probability \& Statistics
  }
\end{itemize}

%-------------------------------------------
\end{document}
