%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[a4paper, top=0.7in, left=0.75in, right=0.75in, bottom=1in]{geometry}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Akhil Shekkari} \\ \vspace{1pt}
     \href{https://shekkari1999.github.io}{\textit{Portfolio}} \textbar\ 
      \href{https://github.com/shekkari1999}{\textit{GitHub}} \textbar\ 
    \href{https://www.linkedin.com/in/akhilshekkari/}{\textit{LinkedIn}} \textbar\ 
    \href{mailto:shekkari.akhil@gmail.com}{\textit{shekkari.akhil@gmail.com}} \textbar\ 
    \href{tel:+1 (425) 426-8292} {+1 (425) 426-8292}
\end{center}

%-----------Professional Summary-----------
\section{Professional Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    
\item \textbf{AI engineer with 3+ years} of industry experience specializing in building production-grade AI systems that are fast, smart, and aligned with human goals. Proven track record of \textbf{training, optimizing, and deploying scalable AI systems}, while ensuring they adhere to ethical guidelines and are aligned with real-world applications.
}
\end{itemize}
   \vspace{-0.7cm}

%-----------SKILLS-----------

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item \textbf{Programming \& Tools:} Python, PyTorch,  SQL, ClearML, Docker, Kubernetes, GitHub actions, Llama parse, Llama index, Lang-chain, Lang-graph, Scikit-learn.
    \vspace{-0.3cm}

    \item \textbf{Cloud \& Infrastructure:} Snowflake, AWS SageMaker, Azure ML, CI/CD.
    \vspace{-0.3cm}

    \item \textbf{Core Competencies:} Deep learning, Generative models, Machine learning,  NLP, RAG, Agentic workflows, Model evaluation, Reinforcement learning.
  }
\end{itemize}
   \vspace{-0.7cm}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Engineer -- Atrium (client: Pfizer) -- Silver Spring, USA}{June 2025 -- August 2025}
      {}{}
      \vspace{-0.65cm}
      \resumeItemListStart
        \resumeItem{Automated key components of \textbf{Statistical Analysis Plan} generation using a \textbf{RAG pipeline}, reducing statisticians' drafting time by \textbf{up to 60\%}.}
        \resumeItem{Architected a custom \textbf{LLM-as-a-Judge} system combining prompting and structured rubric evaluation to detect hallucinations and guideline deviations in generated SAPs with over \textbf{80\% precision}.}
        \resumeItem{Designed \textbf{Prompt Evaluation} experiments by testing variations in temperature, system prompts, and input formatting resulting in a \textbf{20\%} improvement in generation consistency for critical SAP tasks.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer (ML Domain) -- Tezo -- India}{July 2022 -- July 2024}
      {}{}
      \vspace{-0.65cm}
      \resumeItemListStart
        \resumeItem{Built a \textbf{RAG-powered chatbot} integrated with \textbf{SharePoint project repositories}, providing employees a unified interface to query across \textbf{10k+} internal documents including project charters, design specs, and status reports.}
        \resumeItem{Engineered a \textbf{semantic search pipeline with embeddings + vector DB}, reducing document lookup time by \textbf{~60\%} and improving cross-team visibility into ongoing projects.}
        \resumeItem{Extended capabilities with \textbf{LLM-based summarization} of lengthy project documentation, cutting manual review time for managers by \textbf{~35\%} and enabling quicker decision-making.}
        \resumeItem{Containerized and deployed the system with \textbf{Docker + CI/CD}, ensuring smooth secure on-prem access control.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Software Developer (ML Domain) -- Tezo -- India}{July 2021 -- July 2022}
      {}{}
      \vspace{-0.65cm}
      \resumeItemListStart
        \resumeItem{Migrated policy and claims data to \textbf{Snowflake}, streamlining ETL pipelines and reducing average query times by \textbf{~40\%} compared to the legacy warehouse.}
        \resumeItem{Trained \textbf{ML models} to score policies and detect fraudulent claims, improving recall of fraud cases by \textbf{~15\%} and enabling earlier intervention to prevent financial losses.}
        \resumeItem{Built \textbf{SQL and BI dashboards} for stakeholders, cutting manual report preparation time by \textbf{~25\%}, increasing adoption to \textbf{50+ active users}, and improving decision-making speed across actuarial and operations teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-0.2cm}
%-----------RESEARCH AND TECHNICAL CONTRIBUTIONS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
      {\textbf{AI Agent Framework} {\small\href{https://github.com/shekkari1999/Agents}{[GitHub]}}}{2025}
      \resumeItemListStart
        \resumeItem{Built a \textbf{multi-step reasoning agent} from scratch with OpenAI function calling, \textbf{MCP integration} for external tool servers, Pydantic schemas for structured outputs, and sliding-window memory with compaction.}
        \resumeItem{Implemented tool orchestration (web search, code execution, file handling) with \textbf{callback-driven observability} and session persistence via FastAPI backend.}
        \resumeItem{Evaluated on the \textbf{GAIA benchmark} (GPT-4o vs Claude), achieving competitive scores on multi-step real-world tasks.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Building a Reasoning LLM from Scratch} {\small\href{https://github.com/shekkari1999}{[GitHub]}}}{2025}
      \resumeItemListStart
        \resumeItem{Implemented the complete \textbf{post-training pipeline} to turn a base LLM (Qwen-2.5) into a reasoning model — inference-time scaling, self-refinement, and \textbf{GRPO reinforcement learning} — entirely from scratch (no TRL).}
        \resumeItem{Built a custom inference engine with \textbf{KV-cache}, temperature/top-p sampling, and a math evaluation harness with \textbf{SymPy-based symbolic equivalence} checking on GSM8K and MATH benchmarks.}
        \resumeItem{Implemented \textbf{chain-of-thought prompting, self-consistency} (majority voting), and iterative self-refinement with log-probability confidence scoring.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Mini Inference Engine from Scratch} {\small\href{https://github.com/shekkari1999}{[GitHub]}}}{2025}
      \resumeItemListStart
        \resumeItem{Built a modular transformer inference engine from scratch to study LLM serving internals: implemented \textbf{naive, streaming (online softmax), and Triton-fused attention} kernels with benchmarked latency and memory comparisons.}
        \resumeItem{Designed \textbf{paged KV-cache} with on-demand page allocation to eliminate memory fragmentation, and \textbf{contiguous KV-cache} as baseline — benchmarked prefill (4K--16K tokens) and decode throughput across context lengths.}
        \resumeItem{Demonstrated \textbf{O(T) memory} for streaming attention vs O(T\textsuperscript{2}) for naive, and quantified kernel-fusion speedups via Triton over Python-level page loops.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Qwen 3B -- Chat \& Function Calling Finetuning} {\small\href{https://github.com/shekkari1999}{[GitHub]}}}{2025}
      \resumeItemListStart
        \resumeItem{Took the base Qwen 3B model and \textbf{LoRA fine-tuned} it in two stages: conversational data for chat capabilities, then function-calling datasets for structured \textbf{tool use}.}
        \resumeItem{Used \textbf{QLoRA} for memory-efficient training on a single consumer GPU, producing separate LoRA adapters for each stage.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Image Super-Resolution -- ResShift} {\small\href{https://github.com/shekkari1999/DiffusionSR}{[GitHub]}}}{2025}
      \resumeItemListStart
        \resumeItem{Implemented ResShift from scratch: \textbf{U-Net} with 4-stage encoder-decoder and \textbf{Swin Transformer} bottleneck, residual shifting mechanism reducing diffusion steps to just \textbf{15}.}
        \resumeItem{Evaluated using \textbf{PSNR, SSIM, and LPIPS}, achieving competitive results on DIV2K with significantly fewer inference steps than standard diffusion SR.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Code Reviewer -- Knowledge Distillation} {\small\href{https://github.com/shekkari1999/MSML605CodeReviewer}{[GitHub]}}}{2025}
      \resumeItemListStart
        \resumeItem{LoRA fine-tuned a \textbf{220M parameter} Microsoft model on 150k code samples, then \textbf{distilled to 80M parameters}, cutting inference cost by \textbf{~60\%} while maintaining quality.}
        \resumeItem{Containerized with Docker and tracked experiments with \textbf{ClearML} for dataset/model versioning and checkpoint management.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Technical Blogs} {\small\href{https://shekkari1999.github.io/blogs.html}{[Link]}}}{}
      \resumeItemListStart
        \resumeItem{\textbf{Contributor at \textit{Towards AI}}, writing on GPT internals, fine-tuning, and memory-efficient model engineering.}
      \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-0.2cm}
%-----------EDUCATION-----------

\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item \textbf{University of Maryland, College Park} \hfill Expected May 2026 \\
          Master of Science in Applied Machine Learning \\
          \textbf{Relevant coursework:} Probability \& Statistics; Advanced Machine Learning; Deep Learning; NLP; Optimization. \\[-0.2cm]

\end{itemize}
\vspace{-0.6cm}

%-------------------------------------------
\end{document}
